partial: An R Package for Creating Partial Dependence Plots

### 2016-09-01 manuscript/greenwell.tex
minor edits

Currently supported models are described in Table~\ref{tab:models}. While more models will be added as the package grows, the \code{partial.default} method should be able to handle many others not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.
\begin{table}[htbp]
  \begin{tabular}{p{4cm}ll}
    \toprule
      Type of model & R package & Object class \\
      \midrule
      Decision tree             & \CRANpkg{rpart} \citep{rpart-pkg} & \code{"rpart"} \\
                                & \pkg{party}    & \code{"BinaryTree"} \\
                                & \pkg{partykit} & \code{"constparty"}/\code{"party"} \\
      Bagged decision trees     & \CRANpkg{ipred} \citep{ipred-pkg} & \code{"classbagg"}, \code{"regbagg"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"bagging"} \\
      Boosted decision trees    & \pkg{gbm}      & \code{"gbm"} \\
                                & \CRANpkg{xgboost} \citep{xgboost-pkg} & \code{"xgb.Booster"}
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"boosting"} \\
      Random forest & \pkg{randomForest} & \code{"randomForest"} \\
      Conditional random forest & \pkg{party}    & \code{"RandomForest"} \\
                                & \pkg{partykit} & \code{"cforest"} \\
      Linear model              & \pkg{stats}    & \code{"lm"} \\
      Generalized linear model  & \pkg{stats}    & \code{"glm"}, \code{"lm"} \\
      Multivariate adaptive regression splines (MARS) & \CRANpkg{earth} \citep{earth-pkg} & \code{"earth"} \\
      Support vector machine    & \CRANpkg{e1071} \citep{e1071-pkg} & \code{"svm"} \\
                                & \CRANpkg{kernlab} \citep{kernlab-pkg} & \code{"ksvm"} \\
      \bottomrule
  \end{tabular}
  \caption{Models specifically supported by the \pkg{package}.}
  \label{tab:models}
\end{table}

>>>>

% FIXME %%%%%%%%%%%%%%%%%%%%%

Currently supported models are described in Table~\ref{tab:models}. Using the \code{partial.default} method it is still possible to handle many other models not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package. However, for these cases, the user will need to specify additional options in the call to \code{partial}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
  \begin{tabular}{p{4cm}ll}
    \toprule
      Type of model & R package & Object class \\
      \midrule
      Decision tree             & \CRANpkg{rpart} \citep{rpart-pkg} & \code{"rpart"} \\
                                & \pkg{party}    & \code{"BinaryTree"} \\
                                & \pkg{partykit} & \code{"constparty"}/\code{"party"} \\
      Bagged decision trees     & \CRANpkg{ipred} \citep{ipred-pkg} & \code{"classbagg"}, \code{"regbagg"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"bagging"} \\
      Boosted decision trees    & \pkg{gbm}      & \code{"gbm"} \\
                                & \CRANpkg{xgboost} \citep{xgboost-pkg} & \code{"xgb.Booster"}
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"boosting"} \\
      Random forest & \pkg{randomForest} & \code{"randomForest"} \\
      Conditional random forest & \pkg{party}    & \code{"RandomForest"} \\
                                & \pkg{partykit} & \code{"cforest"} \\
      Linear model              & \pkg{stats}    & \code{"lm"} \\
      Generalized linear model  & \pkg{stats}    & \code{"glm"}, \code{"lm"} \\
      Multivariate adaptive regression splines (MARS) & \CRANpkg{earth} \citep{earth-pkg} & \code{"earth"} \\
      Support vector machine    & \CRANpkg{e1071} \citep{e1071-pkg} & \code{"svm"} \\
                                & \CRANpkg{kernlab} \citep{kernlab-pkg} & \code{"ksvm"} \\
      \bottomrule
  \end{tabular}
  \caption{Models specifically supported by the \pkg{package}.}
  \label{tab:models}
\end{table}
